Quantum Oracles - How to Transform Classical Problems into Quantum ones

### 2024-08-01 latex/paper.tex
updated paper

\documentclass{article}
\usepackage{arxiv}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}    
\usepackage{hyperref}      
\usepackage{url}            
\usepackage{booktabs}       
\usepackage{amsfonts}       
\usepackage{nicefrac}       
\usepackage{microtype}      
\usepackage{cleveref}       
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{caption}
\usepackage{braket}
\usepackage{amsmath}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{mathtools}
\usepackage{titlesec}
\usepackage[rightcaption]{sidecap}
\usepackage{wrapfig}

@@

\begin{document}
\maketitle
\begin{abstract}
	Using quantum oracles and other effects, like superposition, \emph{5 mini-projects} were done. The main goal of these projects was to answer if it's possible to bring some problems to the quantum realm and if such translation worth it. After finishing the tests, it was possible to see that, some of the implementations show descent results. However, classical computing is still a fundamental part of quantum algorithms.
\end{abstract}

@@

\begin{center}
	\includegraphics[scale=0.3]{phase_oracle_1.png}
	\captionof{figure}{Phase Oracle using Phase-Kickback Example}
	\label{fig:phase-oracle-1}
\end{center}

@@

\begin{center}
	\includegraphics[scale=0.3]{phase_oracle_2.png}
	\captionof{figure}{Phase Oracle - Minimal Oracle Layout Example}
	\label{fig:phase-oracle-2}
\end{center}

In the example above \ref{fig:phase-oracle-2}, a $MCP$ gate was applied adding a $\pi$ phase and another two $X$ gates were used to invert the Qubits we want to have the value $0$ as a trigger for the $MCP$ phase application. Following the little-endian format the final encoded bit-string is: $011_{2}$ or $3_{10}$.

\begin{center}
	\includegraphics[scale=0.5]{phase_oracle_unitary.png}
	\captionof{figure}{Figure \ref{fig:phase-oracle-2} Resulting Unitary Matrix}
	\label{fig:phase-oracle-unitary}
\end{center}

Looking at its unitary matrix, it's possible to see the $8\times8$ identity matrix with a $-1$ in the column relative to the value $011_{2}$.

\subsubsection{Boolean Oracle}
The Boolean Oracle has a similar structure with the Phase Oracle. However, this time a phase isn't applied, acting this way a regular boolean function, mapping inputs to outputs.

\begin{center}
	\includegraphics[scale=0.3]{balanced-oracle.png}
	\captionof{figure}{Boolean Oracle Example}
	\label{fig:boolean-oracle}
\end{center}

@@

\begin{center}
	\includegraphics[scale=0.3]{minimal-oracle.png}
	\captionof{figure}{Boolean Minimal Oracle example}
	\label{fig:minimal-oracle}
\end{center}

In the previous example \ref{fig:minimal-oracle}, two $SWAP$ gates were used to invert the order of the Qubits values. Like this, the final matrix keeps unitary and reversible.

@@

\subsubsection{Other kinds of Oracles}
In addition to the oracles mentioned above, it's possible come across with different mentions of Oracles, like the Simons's, Deutsch-Jozsa's, etc. However, these are just implementations of models already shown in this paper. Also, the most relevant for the following projects are the Phase and Boolean ones, due that, there's no use to keep discussing about many others sub-categories of Oracles here.
\newpage

@@

%FIX THIS IMAGE%
\begin{SCfigure}[0.45][h]
	\caption{Comparing the Standard Grover's algorithm with the version modifying the rotation angles $[0, 2\pi]$ for each 4 bits bit-string}
	\includegraphics[scale=0.45]{improvement-grover-algorithm-4bits-0-to-2pi.png}
	\label{fig:best-angle-grover}
\end{SCfigure}

>>>>

\documentclass{article}
\usepackage{arxiv}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}    
\usepackage{hyperref}      
\usepackage{url}            
\usepackage{booktabs}       
\usepackage{amsfonts}       
\usepackage{nicefrac}       
\usepackage{microtype}      
\usepackage{cleveref}       
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{caption}
\usepackage{braket}
\usepackage{amsmath}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{mathtools}
\usepackage{titlesec}
%\usepackage[rightcaption]{sidecap}
\usepackage{wrapfig}
\usepackage{subfig}

@@

\begin{document}

\maketitle

\begin{abstract}
	Using quantum oracles and other effects, like superposition, \emph{5 mini-projects} were done. The main goal of these projects was to answer if it's possible to bring some problems to the quantum realm and if such translation worth it. After finishing the tests, it was possible to see that, some of the implementations show descent results. However, classical computing is still a fundamental part of quantum algorithms.
\end{abstract}

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.3]{phase_oracle_1.png}
	\caption{Phase Oracle using Phase-Kickback Example}
	\label{fig:phase-oracle-1}
\end{figure}

@@

\begin{figure}
	\centering
	\subfloat[\centering Phase Oracle - Minimal Oracle Layout Example]{\includegraphics[width=5cm]{phase_oracle_2.png} \label{fig:phase-oracle-2}}
	\subfloat[\centering Figure \ref{fig:phase-oracle-2} Resulting Unitary Matrix]{\includegraphics[width=5cm]{phase_oracle_unitary.png} \label{fig:phase-oracle-unitary}}
	\caption{Phase Oracle Minimal Version}
	\label{fig:phase-oracle-minimal}
\end{figure}

In the example above \ref{fig:phase-oracle-minimal}, a $MCP$ gate was applied adding a $\pi$ phase and another two $X$ gates were used to invert the Qubits we want to have the value $0$ as a trigger for the $MCP$ phase application. Following the little-endian format the final encoded bit-string is: $011_{2}$ or $3_{10}$.

Looking at its unitary matrix \ref{fig:phase-oracle-unitary}, it's possible to see the $8\times8$ identity matrix with a $-1$ value in the column relative to the bit-string $011_{2}$, representing the encoded value.

\subsubsection{Boolean Oracle}

The Boolean Oracle has a similar structure with the Phase Oracle. However, this time a phase isn't applied, acting this way a regular boolean function, mapping inputs to outputs.

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.3]{balanced-oracle.png}
	\caption{Boolean Oracle Example}
	\label{fig:boolean-oracle}
\end{figure}

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.3]{minimal-oracle.png}
	\caption{Boolean Minimal Oracle example}
	\label{fig:minimal-oracle}
\end{figure}

The example \ref{fig:minimal-oracle} shows an Boolean Oracle which two $SWAP$ gates were used to invert the Qubits values order. Doing this way, the final matrix keeps its unitary and reversible properties, once the  $SWAP$ gates act in both Qubits together, mirroring its action.

@@

\subsubsection{Other kinds of Oracles}
In addition to the oracles mentioned above, it's possible come across with different mentions of Oracles, like the Simons's, Deutsch-Jozsa's, etc. However, these are just implementations of models already shown in this paper. Also, the most relevant for the following projects are the Phase and Boolean ones, due that, there's no use to keep discussing about many others sub-categories of Oracles here.

@@

%FIX THIS IMAGE%
%\begin{SCfigure}[0.45][h]
%	\caption{Comparing the Standard Grover's algorithm with the version modifying the rotation angles $[0, 2\pi]$ for each 4 bits bit-string}
%	\includegraphics[scale=0.45]{improvement-grover-algorithm-4bits-0-to-2pi.png}
%	\label{fig:best-angle-grover}
%\end{SCfigure}
